Learning Network Size while Training with ShrinkNets

### 2018-02-09 paper/ICML/introduction.tex

As neural networks become increasingly widely deployed in a variety of
applications  -- ranging from improving camera quality on mobile phones
\cite{googleapple} to language translation \cite{languagetranslation} to text
auto-completion \cite{autocomplete} -- and on diverse hardware architectures
-- from laptops to phones to embedded sensors --  inference performance and
model size are becoming as important in learning as metrics measures of
prediction quality. However, these three aspect of model performance --
quality, performance and size -- are largely optimized separately today, often
with suboptimal results.

@@

In contrast, in this paper we present a new method to simultaneously optimize
both network size and model performance. The key idea is to learn the right
network size at the same time that we optimize for prediction performance for a
specific task. Our approach, called {\it ShrinkNets}, starts with an {\it
oversized} network, and dynamically shrinks it by eliminating unimportant
neurons---those that do not contribute to prediction performance---during
training time. For that, ShrinkNets must detect the unimportant neurons, and
remove them from the network, thus drastically reducing the network size. The
removal of entire neurons and not connections is crucial, because it leads to
dense networks, which lead to better inference performance. To support the
detection and removal of unimportant neurons we introduce a new layer, called
\textbf{Switch layer}. Introducing this new layer means we must redefine the
loss function to account for the sparsity effect it introduces. ShrinkNets has
two main benefits. First, it explores the architecture of models that are both
small and perform well, rather than starting with a high-performance model and
making it small.  This allows us to efficiently generate a family of smaller and
accurate models without an exhaustive and expensive hyperparameter search over
the number of neurons in each layer.  Second, in contrast to existing neural
network compression techniques~\cite{Aghasi2016,han2015deepcompression}, our
approach results in models that are not only small, but where the layers are
dense, which means that inference time is also improved, e.g., on GPUs.

XXX people actually don't treat network size as a hyperparameter;  we do!

@@

In summary, our contributions are as follows: 
\begin{compactenum}
\item We propose a novel technique based on dynamically switching on and off neurons, 
which allows us to optimize the network size as the network is trained. 
\item \srm{xxx postprocessing techniques to strip out switch layers}
\item We show that our technique is a relaxation of group LASSO~\cite{Yuan2006} and prove that our problem admits many global minima.
\item \srm{Some claim about model size vs performance}
\item We demonstrate the efficacy of our technique on both convolutional and fully-connected neural nets,
showing that 
ShrinkNets finds networks within +/-X\% of best hand-crafted accuracy in XX\% of
training time compared to existing hyperparameter optimization methods. \srm{Mention the specific 
model/dataset where this is true.}
\item We demonstrate that ShrinkNets can achieve this accuracy with only YY\% 
of neurons. \srm{This claim should be something about how much smaller a network with say 99\%
accuracy is one some real dataset}
\item \srm{Something about dense networks and then benefit over optimal brain damage}
\item \srm{Some claim about inference time}
\item \srm{Some claim about compatibility with existing compression techniques?}
\end{compactenum}

>>>>

Neural networks are increasingly being deployed in a wide variety  of
applications  and on diverse hardware architectures ranging from laptops to
phones to embedded sensors. This wide variety of deployment settings means
that inference time and model size are becoming as important as  prediction
quality when assessing model performance.  However, these three dimensions of
performance (model quality, inference time and model size)  are largely
optimized separately today, often with suboptimal results.

@@

In contrast, in this paper we present a new method to simultaneously optimize
 network size and model performance. The key idea is to learn the right
network size at the same time that we optimize for prediction performance for a
specific task. Our approach, called {\it ShrinkNets}, starts with an {\it
over-sized} network, and dynamically shrinks it by eliminating unimportant
neurons---those that do not contribute to prediction performance---during
training time. To do this, ShrinkNets must detect the unimportant neurons, and
remove them from the network. The
removal of entire neurons and not connections is crucial, because it leads to
dense networks, which in turn leads to better inference performance. To support the
detection and removal of unimportant neurons we introduce a new layer, called
\textbf{Switch layer}. Introducing this new layer simply requires us to
add a term to the
loss function to optimize the weights of this layer during training. ShrinkNets has
two main benefits. First, it explores the architecture of models that are both
small and perform well, rather than starting with a high-performance model and
making it small.  It does this using a single new hyperparameter that effectively 
models the target network size.  This allows us to efficiently generate a family of smaller and
accurate models without an exhaustive and expensive hyperparameter search over
the number of neurons in each layer.  Second, in contrast to existing neural
network compression techniques~\cite{Aghasi2016,han2015deepcompression}, our
approach results in models that are not only small, but where the layers are
dense, which means that inference time is also improved, e.g., on GPUs.

@@

In summary, our contributions are as follows: 
\begin{compactenum}
\item We propose a novel technique based on dynamically switching on and off neurons, 
which allows us to optimize the network size as the network is trained. 
\item \srm{xxx postprocessing techniques to strip out switch layers}
\item We show that our technique is a relaxation of group LASSO~\cite{Yuan2006} and prove that our problem admits many global minima.
\item We demonstrate the efficacy of our technique on both convolutional and fully-connected neural nets,
showing that 
ShrinkNets finds networks within +/-X\% of best hand-crafted accuracy in XX\% of
training time compared to existing hyperparameter optimization methods. \srm{Mention the specific 
model/dataset where this is true.}
\item We demonstrate that ShrinkNets can achieve this accuracy with only YY\% 
of neurons. \srm{This claim should be something about how much smaller a network with say 99\%
accuracy is one some real dataset}
\item \srm{Some claim about inference time}
\item \srm{Some claim about model size vs performance}
\end{compactenum}
